A Type System for Safe and Scalable Parallelism using Logical Regions \\ (Extended Version)

### 2012-07-15 doc/popl2013full/langdef.tex

\item[E-New]
\item[E-Var]
\item[E-IsNull-F]
\item[E-IsNull-T]
\item[E-Let]
\item[E-Add]
\item[E-Compare]
\item[E-IfElse-T]
\item[E-IfElse-F]
\item[E-Newcolor]
\item[E-Color]
\item[E-UpRgn]
\item[E-DownRgn]
\item[E-Read]
\item[E-Write]
\item[E-Reduce]
\item[E-Pack]
\item[E-Unpack]
\item[E-Call]
\item[E-Program]

>>>>

\item Case[E-New].
By assumption, 
$\opsenv{\text{new }T@r}{l}{[]}$ and 
$\typeenv{\text{new }T@r}{T@r}$ and 
$\mapconsist{\Omega}$ and 
$\localconsist{L}{\Gamma}$ and 
$\storeconsist{S}{H}$.
The hypothesis of the [E-New] rule is that $l \in M(r)$ and $H(l) = M \llbracket T \rrbracket$,
which establishes $\valueconsist{l}{T}$.  
The other two conclusions,
$\traceconsist{[]}$ and 
$\privconsist{[]}{\Phi}$, follow trivially.
\item Case [E-Var].
By assumption, 
$\opsenv{id}{v}{[]}$ and 
$\typeenv{id}{T}$ and 
$\mapconsist{\Omega}$ and 
$\localconsist{L}{\Gamma}$ and 
$\storeconsist{S}{H}$.
The hypothesis of the [E-Var] rule is $L(id) = v$.
From $\localconsist{L}{\Gamma}$ we have $\valueconsist{L(id)}{\Gamma(id)}$.
The hypothesis of the [T-Var] rule is $\Gamma(id) = T$.
Putting these three facts together we conclude $\valueconsist{v}{T}$.
The other two conclusions,
$\traceconsist{[]}$ and 
$\privconsist{[]}{\Phi}$, follow trivially.

\item Case [E-IsNull-F].
By assumption, 
$\opsenv{\text{isnull}(e)}{\textit{false}}{E}$ and 
$\typeenv{\text{isnull}(e)}{bool}$ and 
$\mapconsist{\Omega}$ and 
$\localconsist{L}{\Gamma}$ and 
$\storeconsist{S}{H}$.
From the form of [E-IsNull-F] we know that
$\opsenv{e}{l}{E}$, and
and from the form of the type rule [T-IsNull] we know
$\typeenv{e}{T@(\oton{r})}$.
Clearly $\valueconsist{\textit{false}}{bool}$, and
$\traceconsist{E}$ and 
      $\privconsist{E}{\Phi}$ follow by induction.

\item Case [E-IsNull-T] is almost identical to case [E-IsNull-F], with $l$ replaced by \textit{null} and
\textit{true} replaced by \textit{false}.

\item[E-Let]
\item[E-Add]
\item[E-Compare]
\item[E-IfElse-T]
\item[E-IfElse-F]
\item[E-Newcolor]
\item[E-Color]
\item[E-UpRgn]
\item[E-DownRgn]
\item[E-Read]
\item[E-Write]
\item[E-Reduce]
\item[E-Pack]
\item[E-Unpack]
\item[E-Call]
\item[E-Program]
